### 2013-05-14 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
starting work on breakdown analysis and adding sections to the concluding chapter

\subsection{Preliminary Jacobi Preconditioned Calculations}
\label{subsec:jacobi_prec_assembly_calc}
Based on the success of block Jacobi preconditioning with the test
problem used for the spectral radius parameter study, we use it first
to solve the $17 \times 17$ fuel assembly problem. A single energy
group problem was first solved with $SP_1$ discretization, effectively
giving the one-speed neutron diffusion system for the fuel assembly
resulting in 20,088 degrees of freedom in the
problem. Figure~\ref{fig:block_jacobi_res_mcsa} gives the residual
infinity norm as a function of iteration for the MCSA linear solve in
the first eigenvalue iteration.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=5in]{chapters/spn_equations/block_jacobi_res.pdf}
  \end{center}
  \caption{\textbf{Residual infinity norm vs. iteration for the block
      Jacobi preconditioned MCSA solve during the first eigenvalue
      iteration of the 1-group $17 \times 17$ fuel assembly problem.}
    \textit{Convergence was not achieved with the block Jacobi
      preconditioned method.}}
  \label{fig:block_jacobi_res_mcsa}
\end{figure}
Convergence was not achieved as noted by the rapid rise in the
residual over a few iterations. Based on the spectral radius
computations performed, these results are not in line with
expectations for this problem. Even if the problem may be
ill-conditioned, we do expect convergence of MCSA. To investigate
further, a block Jacobi preconditioned Richardson iteration was used
to solve the same problem. Figure~\ref{fig:block_jacobi_res_richardson}
gives the residual infinity norm as a function of iteration for the
Richardson linear solve in the first eigenvalue iteration.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=5in]{chapters/spn_equations/block_jacobi_rich_res.pdf}
  \end{center}
  \caption{\textbf{Residual infinity norm vs. iteration for the block
      Jacobi preconditioned Richardson solve during the first
      eigenvalue iteration of the 1-group $17 \times 17$ fuel assembly
      problem.}  \textit{A spectral radius near 1 was observed for the
      iteration matrix.}}
  \label{fig:block_jacobi_res_richardson}
\end{figure}
Poor converge is observed for the Richardson iteration, however,
convergence is achieved meaning that the criteria needed to satisfy
MCSA convergence has also been met. The effective slope of the
convergence curve in Figure~\ref{fig:block_jacobi_res_richardson} will
give an approximation for the spectral radius via
Eq~(\ref{eq:linear_k_iter_norm3}). For the data in
Figure~\ref{fig:block_jacobi_res_richardson}, $\rho(\mathbf{H})
\approx 0.985$, nearing the limits of MCSA applicability and well
beyond the spectral radii generated in the initial spectral analysis.

@@

\subsubsection{MCSA Breakdown Analysis}
\label{subsubsec:breakdown_analysis}

@@

%%---------------------------------------------------------------------------%%
\section{Multiple Fuel Assembly Challenge Problem}
\label{sec:spn_challenge_problem}

>>>>

\subsection{Preliminary Jacobi Preconditioned Calculations}
\label{subsec:jacobi_prec_assembly_calc}
Based on the success of block Jacobi preconditioning with the test
problem used for the spectral radius parameter study, we use it first
to solve the $17 \times 17$ fuel assembly problem. A single energy
group problem was first solved with $SP_1$ discretization, effectively
giving the one-speed neutron diffusion system for the fuel assembly
resulting in 20,088 degrees of freedom in the
problem. Figure~\ref{fig:block_jacobi_res_mcsa} gives the residual
infinity norm as a function of iteration for the MCSA linear solve in
the first eigenvalue iteration using 25,000 stochastic histories at
every iteration for the adjoint Neumann-Ulam solve.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=5in]{chapters/spn_equations/block_jacobi_res.pdf}
  \end{center}
  \caption{\textbf{Residual infinity norm vs. iteration for the block
      Jacobi preconditioned MCSA solve during the first eigenvalue
      iteration of the 1-group $17 \times 17$ fuel assembly problem.}
    \textit{Convergence was not achieved with the block Jacobi
      preconditioned method.}}
  \label{fig:block_jacobi_res_mcsa}
\end{figure}
Convergence was not achieved as noted by the rapid rise in the
residual over a few iterations. Based on the spectral radius
computations performed, these results are not in line with
expectations for this problem. Even if the problem may be
ill-conditioned, we do expect convergence of MCSA. To investigate
further, a block Jacobi preconditioned Richardson iteration was used
to solve the same problem. Figure~\ref{fig:block_jacobi_res_richardson}
gives the residual infinity norm as a function of iteration for the
Richardson linear solve in the first eigenvalue iteration.
\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=5in]{chapters/spn_equations/block_jacobi_rich_res.pdf}
  \end{center}
  \caption{\textbf{Residual infinity norm vs. iteration for the block
      Jacobi preconditioned Richardson solve during the first
      eigenvalue iteration of the 1-group $17 \times 17$ fuel assembly
      problem.}  \textit{A spectral radius near 1 was observed for the
      iteration matrix.}}
  \label{fig:block_jacobi_res_richardson}
\end{figure}
Poor converge is observed for the Richardson iteration, however,
convergence is achieved meaning that the criteria needed to satisfy
MCSA convergence has also been met. The effective slope of the
convergence curve in Figure~\ref{fig:block_jacobi_res_richardson} will
give an approximation for the spectral radius via
Eq~(\ref{eq:linear_k_iter_norm3}). For the data in
Figure~\ref{fig:block_jacobi_res_richardson}, $\rho(\mathbf{H})
\approx 0.985$, nearing the limits of MCSA applicability and well
beyond the spectral radii generated in the initial spectral analysis.

@@

\subsubsection{MCSA Breakdown Analysis}
\label{subsubsec:breakdown_analysis}
For each solver and estimator combination, the spectral radius of the
iteration matrix was varied by changing the absorption cross section
while fixing the grid size and scattering cross section. At each
solve, a minimum of stochastic history per degree of freedom (DOF) in
the problem was used to compute the Monte Carlo correction. If the
solver could not converge in less than 100 iterations, the number of
histories was increased by increments of 5,000 until convergence was
achieved.

@@
